%ब
\section{Cloud Computing} \label{s:cloudComputing}
Cloud computing is a major paradigm that is rapidly shifting the way \ac{IT}
services and tools are being used in the industry.  It is perceived that cloud
computing would help extend the capabilities of many \ac{IT} and online services
without the need for costly infrastructure.

Similar to remote computing where other machines or computers are accessed from
the local machine through a network,   cloud computing leverages network
connections to provide various services to the users.  It also brings with it
the virtualization of applications and services,   where it appears to users as
if the applications are running on the user's machine rather than a remote cloud
machine~\citep{cloudcomputingdefined}.  This removes the need for
installing the actual software by the users.  Thus,   both expert and naive
users need not worry about the technical details and configurations to use these
cloud services.

Cloud computing is generally based on a subscription model where users pay as
per their usage,   which is very similar to utility services like electricity,  
gas or water etc.  The coalescence of virtualization,   where applications are
separated from the infrastructure is what makes cloud computing easy to use.
Users do not have to invest in software applications as they can access such
applications on the cloud.  Users pay only for the services they use.  For
example,   they pay only for the amount of storage their cloud database uses or
pay only for the bandwidth consumed by the servers they rent from the cloud
providers.  Applications and databases are stored in large server farms or data
centres owned by companies like Google,  IBM etc.

The architecture of cloud computing services has users who avail cloud services
as the front-end. A user is any hardware or software application that relies on
cloud computing to perform its work. Notice that 'users' represent the
end-users,   like  database administrators or programmers or anyone who benefits
from cloud computing services while 'client' refers to any software applications
or \acp{API}  that are used to perform cloud computing. The back end of the
cloud architecture includes the cloud servers, databases,   and computers etc. ,
which are abstracted from users.  All the components like the servers,
applications, the data storages work together through a web service to provide
the users with the cloud services.

The overall structure of cloud computing and its various services have been
generalised into layers~\citep{Buyya,Spring1,Spring2}.

\begin{description}
	\item [\acf{SaaS}] is the service provided by the cloud
	providers where users do not have to install the software applications. 
	
	\item [\acf{PaaS}] is the service where a hardware or
	software platform is provided to users.  A platform could be an operating system,  
	programming environment,   hardware,   run-time libraries etc. 
	
	\item [\acf{IaaS}] is the service where users can use
	the expensive hardware like network equipments,   servers etc. 
	
	\item [\acf{DaaS}] is a cloud storage service  that represents
	the storage facilities,   like  \acp{DBMS} which are provided
	as cloud services for which users pay only for the storage space they
	use~\citep{Mateljan,Wuetal}.

\end{description}


\ac{DaaS} involves hosting cloud databases in the cloud which offer data
management,   data retrieval,   and other database services.  Due to the
increasing number of users deploying and using web applications on cloud, cloud
databases form a crucial part to store the increasing amounts of data on the
cloud.  Many companies like Amazon,   Google,   IBM,   and Microsoft provide
\ac{DaaS} and offer varying levels of services~\citep{Mateljan}. The next
section gives a description about cloud databases and its key features.


