%ब
\chapter{Design of Referential Integrity Constraints in NoSQL
databases} \label{c:solutions}

% As mentioned previously,    cloud column-oriented key-value \acp{DBMS} lack
% referential integrity constraints to maintain foreign key relationships,    as
% seen in traditional \acp{RDBMS},    due to its non-relational data model.    
% Moreover,    these cloud \acp{DBMS} do not normalise data nor maintain
% relationships.   
Traditionally,   referential
integrity constraints are imposed on data items of a database to maintain
foreign key relationships.    These relationships are
 maintained by correctly identifying and preserving the data dependencies 
 existing between the data items.   
% Traditionally,   foreign key relationships are
% maintained by correctly identifying and preserving the data dependencies existing between data items in a database.   
% These dependencies are maintained and  validated by imposing referential
% integrity constraints on data items.    
Most popular traditional \acp{RDBMS}
preserve such dependency information in their \texttt{System} tables or data
dictionaries.     These tables store the necessary information  which is required
to maintain valid dependencies.    The information stored in such tables include table
names,    primary and foreign keys,  among others.   
This can be seen in popular \acp{RDBMS} like  MS SQL Server,    PostgreSQL,  
Oracle,   and so on.     

For example,    in MS SQL Server 2000,   \texttt{sysforeignkeys} is a
\texttt{System} table which stores the information of all foreign keys of every
table in a database,   and \texttt{sysreferences} stores the mappings of  foreign
keys to the referenced primary key columns \citep{msdn}.  Information in these
\texttt{System} tables consist of  the names of tables and its constraints, 
unique identifiers of referenced and referencing columns and others.  In
PostgreSQL,   such information is presented to users as views but it is stored in
base tables which contain the dependency information of data items in a
database.  The view \texttt{table\_constraints} show the information about all
the constraints in every table owned by the current user~\citep{postgres}. 
Similarly,   Oracle uses a \texttt{SYSTEM} meta-database to hold such constraint
information.   In general,   \texttt{System} tables or views with information
about the existing dependencies  are looked up by these \acp{RDBMS} whenever
referential integrity checks are triggered \citep{msdn}. 


The solutions presented in this thesis save the dependency information as
metadata.    This metadata contains relevant  information about primary keys of
column families and foreign key relationships in keyspaces.   Thus,  metadata is
accessed whenever an operation is performed on the data and referential
integrity needs to be validated.  These solutions are implemented using an
experimental \ac{API} which is discussed in Chapter~\ref{c:Implementation}. 


This chapter presents the design of  four  solutions  that implement referential
integrity constraints in a cloud \ac{NoSQL} \ac{DBMS}.   
Section~\ref{s:design-Metadata} describes the metadata used by the solutions 
 to store the dependency information.    Section~\ref{s:design-sol1}, 
 ~\ref{s:design-sol2}, ~\ref{s:design-sol3}, ~\ref{s:design-sol4}  present
 the design and motivation of the four solutions. 
%  of the first solution.   
%  Section presents Solution~2 and its design and motivation.    Section describes the design
%  and motivation of Solution 3.    Section presents the design
%  and motivation of Solution~4.   
Section~\ref{s:Design-summary}
 summarises the design of the four solutions.   
 % Section~\ref{s:API} describes the design and implementation of the experimental
% API developed to integrate all the four
% solutions.    
% Section~\ref{s:sol1} describes  the first solution,   which implements
% referential integrity constraints by saving metadata along with the actual data.   
% Section~\ref{s:sol2} describes the second  solution where metadata is
% saved as a top row.    Section~\ref{s:sol3} describes the third   
% solution which saves metadata separate from the actual data.      
% Section~\ref{s:sol4}  describes the fourth solution which saves metadata in a separate cluster.   
% Finally,   Section~\ref{s:solutions-summary} presents a brief summary of this
% chapter.    

\input{chapter/Design-Metadata}

\input{chapter/Design-Solution1}

\input{chapter/Design-Solution2}

\input{chapter/Design-Solution3}

\input{chapter/Design-Solution4}



\section{Summary}\label{s:Design-summary}
The main difference in the design of all the  solutions is the way each of the
solutions store metadata.    Solution~1 stores metadata with the data in every
super column providing fast access to the metadata but increasing its
redundancy. 
Solution~2 has a similar approach as Solution~1 but stores metadata in a single
super column in every column family.   This approach is useful when the metadata
is large since it consumes less space when compared to Solution~1. 
Both Solutions~1 and 2 use special characters in the metadata in order to
distinguish the  constraints relevant to an entity. 
Solution~3 separates the metadata from the actual data and stores all the
constraints together for all column families of a keyspace  in a centralised
way.    This is useful when metadata has to be  altered because it simplifies the
management of metadata.  
Solution~4 has a similar approach as Solution~3,  but saves the \texttt{Metadata}
column family in a separate cluster on different nodes.    It also caches the
metadata  to save operational time and reduce database connections to a
different cluster. 

The next chapter presents the  experimental \ac{API} which provides methods for
 retrieving and processing the metadata as well as handling all the \ac{CRUD}
 operations and referential integrity validations.  

% Since metadata storage is unique in each  solution,  The way metadata is accessed
% and processed are different in each of the solutions.   
%  As mentioned previously,  the experimental \ac{API} provides methods for
%  retrieving and processing the metadata and  handles all the \ac{CRUD}
%  operations as well as the referential integrity validations.  This is 
%  discussed in the next chapter.  

% Thus,   this
% solution differs from Solution~1 only in the way the metadata is stored to improve resource
% utilisation and the way special characters are used and saving only the
% relevant constraints for a column family are  the same as in Solution~1.   
% It also explains how each of the solutions retrieves and processes the
% metadata.   

% The insert,   update and delete operations are performed similar to the other
% solutions.   


% These methods and all the
% solutions are incorporated  into an experimental \ac{API},   which is
% described in Chapter~\ref{c:Implementation}.   
