\chapter{Introduction} 
Cloud computing is a major paradigm that is rapidly shifting the way IT services
and tools are being used.  %Services and applications are hosted on the internet
% and users avail them according to their needs. 
It offers economic benefits in infrastructure,  operating systems,  \acp{DBMS}  and
other resources as these are hosted on the Internet and provided as cloud
services which users avail  according to their needs. 
% For these resources,  users pay only for what they use and do not have to
% invest in buying expensive hardware or install operating systems,  while they
% can avail these inexpensively from the cloud. 
This leads to reduced maintenance costs,  automation of common tasks,  global
access,  and many other advantages.  
% For these advantages,  cloud soon became a
% strong backbone for many applications and encouraged the migration of more
% applications as well as  data storage to the cloud.  Also,  it  promoted many
% novel theories and applications to enhance cloud (\todo{cite
% (Wilkes, 2010)} ). 
For these advantages,  it is natural for the cloud to be the
backbone of  many applications 
point of  encouraging the migration of other  applications  as well as data storage to the cloud.  Also,  it  promoted many novel
theories and applications to enhance cloud (\todo{cite (Wilkes, 2010)} ). 

Cloud computing has been evolving and adapting to offer many different
services.  Cloud data storage is an important part of it which is progressing
alongside. 
The demand for scalable,  efficient and consistent data storage mechanisms has
been increasing as more applications  and users store their data  on the cloud, 
rather than buying and maintaining database servers \todo{cite SNIA}  . 



Cloud \acp{DBMS}   need to satisfy requirements that are exclusive and essential
in a distributed environment.  Some of the expected features in these \acp{DBMS} 
are the scalability to match the increase and decrease of active users, 
robustness by maintaining several copies of data,  flexibility to store
unstructured data,  availability of data despite failures, ability to store large
amounts of data,  consistency even during  concurrent operations and many other
features.  Most of these features are inherent in distributed environments and
are not necessarily addressed by traditional \acp{RDBMS} .  \acp{RDBMS}  get really
complex when it comes to scaling to multiple nodes as these are best suited to
run on a single node and  manipulating or accessing data spread on multiple
nodes becomes complicated involving complex queries. This is mainly due to
normalisation,  as data is not duplicated.  This adversely affects robustness in
cloud as well.  Since \acp{RDBMS}  enforce rigid schema or structure for
databases,  flexibility of storing unstructured data on the cloud will be limited. 
Data is available and consistent in \acp{RDBMS}  as long as the single node it is
designed to run on is alive,  but this can also
be a single point of failure causing complete unavailability of data. 
% users,  high data availability  despite failures,  replication of data on
% several machines,  support of high volumes of data and data consistency even
% during concurrent operations and many other features. 
% These features are different to the ones offered by popular and commonly used
% traditional \acp{RDBMS}  where ACID properties,  normalised and non redundant
% data,  rigid schemas,  efficient query support make these \acp{DBMS}  efficient, 
% but in a non distributed environment. 
% While these traditional \acp{DBMS}  come with a rich set of features,  these
% features hinder its adaptability on the cloud.  For example,  normalisation of
% data prevents data replication as it removes redundancy in data and rigid
% schemas reduce the flexibility of storing unstructured data on cloud. 
% Scalability  is affected poorly due to ACID properties which attempt to
% prevent concurrent operations to make data consistent and isolated. 
Such problems led to the rise of many Cloud \acp{DBMS}  with different data
models and architectures supporting a wide array of cloud adaptable features. 
However,  \acp{RDBMS}  have the desirable feature of referential integrity
constraints,  which is not currently applied in cloud column-oriented key-value
\acp{DBMS} . 

Column-oriented key-value \acp{DBMS} on the cloud are called cloud
\ac{NoSQL}  \acp{DBMS}  or just cloud \ac{NoSQL}  databases and are fundamentally
different from  traditional \acp{RDBMS} . These \acp{DBMS}  support many features
required in cloud,  such as elastic scalability to match varying user
demands, data replication,  schema-less data storage ,   and many other features. 
These \acp{DBMS}  are still evolving and introducing new features in their
architecture and becoming specialised to solve specific cloud data storage
issues.  However,  these \acp{DBMS}  are susceptible to poor data integrity as
these do not normalise data nor maintain relationships.  These \acp{DBMS}  lack
integrity constraints that validate the correctness of data as seen in
traditional \acp{RDBMS}  and one  important integrity constraint absent in most
cloud \ac{NoSQL}  \acp{DBMS}  is the Referential Integrity Constraint.  These
constraints  ensure that relationships between data items are preserved
and maintained in databases and prevent any data operations that violate the
integrity between data items. Without such constraints,  data could be inconsistent and unreliable. 

% Databases on cloud adopt data models and database architecture that are still
% evolving and very different from the popular and traditional data models like
% relational data model. 
% 
% While cloud \ac{NoSQL}  \acp{DBMS}  support many  features suitable to the cloud, 
% it comes with a few disadvantages like poor data integrity,  less security, 
% limited functionalities and others. 


 But it is common to find relationships or dependencies between data in the
 business world and these have to be preserved when it is modelled in the cloud
 environment too. 
 % upon storage in cloud \ac{NoSQL}  database systems too. 
The replicated and distributed nature of the cloud \ac{NoSQL}  \acp{DBMS}  makes
maintaining data dependencies complex and unfeasible in terms of speed and efficiency. 
Thus,  referential integrity constraints to help preserve such dependencies are
not offered by these \acp{DBMS}  and are left for the users to implement at the
application layer instead.  This could mean immense
workload for the application since cloud databases commonly have
 large amounts of interconnected ,  dependant and
widely replicated data,  which is usually spread across several data centers. 
Handling such data where
dependencies have to be correctly maintained and preserved becomes a critical
problem for applications. 

Inspired by such problems of data dependencies,  this thesis studies the existing
modelling of data dependencies in cloud \ac{NoSQL}  \acp{DBMS}  and contributes by
suggesting four solutions so that referential integrity is effectively
maintained , without sacrificing any existing benefits,  in these \acp{DBMS} . 
These solutions extend the consistency of data relationships,   ensuring  data
integrity even when it is widely replicated or spread on different data-centers. 
Additionally,  it reduces the workload of the applications by delegating the
responsibility of validating referential integrity to the \ac{DBMS} . 



\section{Objectives} 

This thesis  focuses particularly on the column-oriented
key-value \acp{DBMS}  on the cloud.  Four  solutions 
using different metadata management techniques are suggested to incorporate
referential integrity constraints in such \acp{DBMS} .  These
solutions are implemented and tested on Cassandra, popular and
prominent column-oriented key-value \ac{DBMS}  in the cloud. 

The performance of these solutions is assessed  in terms of response time and
throughput.  All the proposed solutions  improve data integrity
and  preserves the data dependencies,  regardless of scalability and workload on
the \ac{DBMS} . 

The general objective of this thesis is to incorporate validation mechanisms for
referential integrity in column-oriented key-value \acp{DBMS}.  

The specific objectives of this thesis are:
\begin{itemize} 
  \item Design four solutions to implement referential integrity constraints
  using metadata in various ways to store the information about data
  dependencies. 
  \item Develop an \ac{API}  to implement the four solutions in one of the
  existing column-oriented key-value \acp{DBMS} .  
  \item Analyse the performance of the solutions to determine their
   feasibility and practicality. 
\end{itemize} 

The main contributions of this thesis are an \ac{API}  that can be
used as an interface to implement referential integrity constraints in cloud
column-oriented key-value \acp{DBMS}  and a performance evaluation about the
implementation of the four approaches used in the \ac{API}   in
Cassandra. 

\section{Organization} 

The remainder of this thesis is structured as follows.  Chapter \textmd{2} 
presents cloud computing and describes the column-oriented data model,  its
challenges and the general architecture of Cassandra on which the solutions are
implemented and tested. 
Chapter 3 describes the design of the proposed solutions along with the
motivation for the design and the implementation of these solutions in
Cassandra.  Chapter 4 details the experiments performed to measure the
performance of the solutions.  Chapter 5 presents the analysis of the results
from the experiments.  Chapter 6  presents the conclusions and ideas for future
work
